---
title: "VistaMilk"
runtime: shiny
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    logo: img/logo3.png
---

```{r setup, include=FALSE}
library(flexdashboard)
library(lubridate)
library(shiny)
library(plotly)
library(tidyverse)
library(htmltools)
library(ggpubr)
```

<style>                     
.navbar {
  background-color:#002244;
  border-color:#002244;
}
.section.sidebar {
  background-color: #03C988;
  color:white;

}

.navbar .navbar-nav > .active > a,
.navbar .navbar-nav > .active > a:hover,
.navbar .navbar-nav > .active > a:focus,
.navbar .navbar-nav > li > a:hover,
.navbar .navbar-nav > li > a:focus{
    background: #03C988;
}

.nav-tabs-custom > .nav-tabs > li.active {border-top-color: #00ABC1}
}

</style>  

```{r data_functions, cache=TRUE}
bio <- read.csv("Data/bio.csv")
ncows <- nrow(bio)
AX3 <- vector('list', ncows)
for(i in 1:ncows){
  AX3[[i]] <- read.csv(paste0("Data/AX3_",bio[i,1],".csv"), as.is = T)
  AX3[[i]]$DateTime <- as_datetime( AX3[[i]]$DateTime, format = "%d/%m/%Y %H: %M: %S")
}
breeds <- unique(bio["breed"])
coat_colrs <- unique(bio["coat_color"])
pens <- unique(bio["pen"])
sex <- c('M', 'F')
calves <- unique(bio["calf_ID"])
curr_date <- max(ymd_hms(AX3[[1]][["DateTime"]]))

colrs_sch <- read.csv("Data/color_scheme.csv")
colrs_sch <- colrs_sch[order(colrs_sch$behaviours),]
behaviours <-  colrs_sch$behaviours
colrs_sch = colrs_sch$colour

behaviours_metrics <- read.csv("Data/behaviour_metrics.csv")
behaviours_metrics <- behaviours_metrics[order(behaviours_metrics$behaviour),]
behaviours_metrics$Date <- as_date(behaviours_metrics$Date, format = "%d/%m/%Y")

welfare_score <- read.csv("Data/welfare_score.csv")
welfare_score$Date <- as_date(welfare_score$Date, format = "%d/%m/%Y")

welfare_alert <- read.csv("Data/metadata_welfare_alert_v2.csv")
welfare_alert$Date <- as_date(welfare_alert$Date, format = "%d/%m/%Y")

```


```{r reactive}
get_calf_data <- reactive({
  df <- AX3[[which(bio[,1] == as.integer(input$calfID))]]
  df <- df %>% filter(as_date(DateTime) == as_date(input$date))
  return(df)
})

get_calf_bio <- reactive({
  df <- bio %>% filter(calf_ID == input$calfID)
  return(df)
})

get_act_summ <- reactive({
  df <- AX3[[which(bio[,1] == as.integer(input$calfID))]]
  df <- df %>% filter(as_date(DateTime) == as_date(input$date))
  df <- as.data.frame(table(df$label))
  return(df)
})

get_behv_met <- reactive({
  df <- behaviours_metrics 
  df <- df %>% filter(Date == as_date(input$date) & calf == as.integer(input$calfID))
  df$time_budget_perc = round(df$time_budget/sum(df$time_budget),2)*100
  return(df)
})

get_welfare_score <- reactive({
  df <- welfare_score
  df <- df %>% filter(Date == as_date(input$date) & calf == as.integer(input$calfID))
  return(df)
})

get_welfare_alert <- reactive({
  df <- welfare_alert
  df <- df %>% filter(Date == as_date(input$date) & calf == as.integer(input$calfID))
  df <- df$alert
  return(df)
  })

```



Calves Stats
=====================

Inputs {.sidebar}
-----------------------------------------------------------------------
```{r select_calf}
 selectInput("calfID", label = h3("Calf"), 
    choices = calves, 
    selected = calves[1])
```

```{r select_date}
dateInput("date", label = h3("Date"), value = curr_date, min = "2023-03-07", max = "2023-03-09")
```


Row {data-height=180}
---------------------

### 

```{r}
output[["image"]] <- renderImage({
  calf_bio <- get_calf_bio()
  jpgfile <- paste0("img/cattles/",calf_bio$calf_ID[1],".jpg")
  # style = "margin: 0px; padding: 0px; align: center"
  # img(jpgfile, align = "center")
  div( img(jpgfile), style = "display: block; margin-left: auto; margin-right: auto;")
  width  <- session$clientData$output_image_width
  height <- session$clientData$output_iamge_height
  img(jpgfile, height = height, width = width)
  list(src = jpgfile, height = height, width = width, align="center")
})
imageOutput("image")
```

###

```{r}
renderValueBox({
  calf_bio <- get_calf_bio()
  dob <- calf_bio$DOB
  valueBox(h3("Date of birth (Age in weeks)"), 
           value = paste0(dob," (", as.integer((today() - dmy(dob))/7)," weeks)"), 
           color = "#0F6C7B")
})
```

###

```{r}
renderValueBox({
  calf_bio <- get_calf_bio()
  calf_breed <- calf_bio$breed
  valueBox(h3("Calf Breed (Sex)"), 
           value = paste0(calf_breed, " (", as.character(calf_bio$sex),")"),
           color = "#0F6C7B")
})
```

###

```{r}
renderValueBox({
  calf_bio <- get_calf_bio()
  calf_colrs <- calf_bio$coat_color
  valueBox(h3("Coat Color"), 
           value = calf_colrs, 
           color = "#0F6C7B")
})
```

###

```{r}
renderValueBox({
  calf_bio <- get_calf_bio()
  calf_pen <- calf_bio$pen
  valueBox(h3("Pen Number"), 
           value = calf_pen, 
           color = "#0F6C7B")
})
```





Row {.tabset .tabset-fade}
---------------------

### **Welfare Alert**
```{r alert}

renderTable({
  table_ <- get_welfare_alert()
  head(table_, n = 5)
})
```


### **Raw Activity Data**

```{r raw_plot}
renderPlotly({
  calf_data <- get_calf_data()
  calf_data$ind <- 1:nrow(calf_data)
  fig <- plot_ly(x=~(calf_data$DateTime), y =~ calf_data$Amag, type = "scatter", mode = "lines")
  fig <- fig %>% layout(font = list(family = "Arial", size = 20), 
                        xaxis = list(title = 'Time'),
                        yaxis = list(title = 'Acceleration'))
})

```


### **Behaviour Over Time**

```{r time_plot}

renderPlot({
  calf_data <- get_calf_data()
  fig3 <- ggplot(calf_data, aes(x = (calf_data$DateTime), y=Amag)) + 
  geom_line(aes(colour=color, group=1), size = 1.25) + 
  scale_colour_identity( name = "Behaviours", label = behaviours, breaks = colrs_sch, guide = "legend") + 
  labs(x = "Time", y = "Acceleration")+ 
  # scale_color_manual(name='Behaviour',
  #                    breaks=behaviours,
  #                    values = c("Grooming" = "#64e2a2", "Sniffing/exploring" = "#00194C", "Resting lying" = "plum", "Eating" = "#0F6C7B", "Ruminating"="#7ABC32", "Resting Standing"="lightcoral", "Playing"="#12A1C8" ))+
  theme(text = element_text(size = 20))
  fig3
    
})

```



### **Behaviour Summary**


```{r pie_chart}

renderPlot({
  calf_behv_met <- get_behv_met()
  
  p1 <- ggplot(calf_behv_met, aes(behaviour, bouts_number, fill = behaviour))+
    geom_bar(stat = "identity") + 
    ggtitle("Number of Sessions")+xlab  ("")+ ylab("Number of Sessions")+
    theme_bw()+
    coord_flip()+
    scale_fill_manual(values = colrs_sch)+
    geom_text(aes(y = bouts_number + 3, label = bouts_number), color = "black", size = 5)+
    theme(legend.position = "none", 
          panel.border = element_blank(), 
          plot.title = element_text(size = 15, face = "bold",hjust = 0.5),
          axis.ticks.y = element_blank(),
          axis.title.x = element_text(size = 15),
          axis.text.y = element_text(size = 15, face = 'bold'))
  
  
  p2 <- ggplot(calf_behv_met, aes(behaviour, bouts_duration, fill = behaviour))+
    geom_bar(stat = "identity") + 
    ggtitle("Average Session Duration")+xlab  ("")+ ylab("Minutes")+
    theme_bw()+
    coord_flip()+
    scale_fill_manual(values = colrs_sch)+
    geom_text(aes(y = bouts_duration + 3, label = round(bouts_duration,2)), color = "black", size = 5)+
    theme(legend.position = "none", 
          panel.border = element_blank(), 
          plot.title = element_text(size = 15, face = "bold", hjust = 0.5),
          axis.ticks.y = element_blank(),
          axis.title.x = element_text(size = 15),
          axis.text.y = element_blank())
    
  p3 <- ggplot(calf_behv_met,aes(x = "", y = time_budget_perc, fill = behaviour))+
    geom_col(color = "white")+
    ggtitle("Time Budget")+
    coord_polar(theta = "y") +
    geom_text(aes(label = paste0(time_budget_perc,"%", sep = "")),
              position = position_stack(vjust = 0.5), col = "white", size = 5) +
    theme_void() +
    scale_fill_manual(values = colrs_sch)+ 
    theme(plot.title = element_text(size = 15, face = "bold", hjust = 0.5),
          legend.position="bottom", legend.direction="vertical", 
          legend.text = element_text(size = 13),
          legend.title = element_text(size = 15))
  
  
  
  ggarrange(p3, p1, p2, nrow = 1, widths = c(1,1.2,1))
})
```


### **Welfare Status**

```{r welfare_score}
renderPlotly({
  calf_welfare <- get_welfare_score()
  fig <- plot_ly(
    type = "indicator",
    mode = "gauge+number",
    value = calf_welfare$score[1],
    title = list(text = "Welfare Score", font = list(size = 25)),
    gauge = list(
      axis = list(range = list(NULL, 4), tickwidth = 1, tickcolor = "#00688B"),
      bar = list(color = "#00688B"),
      bgcolor = "white",
      borderwidth = 2,
      bordercolor = "gray",
      steps = list(
        list(range = c(-1, 1), color = "#8B0000"),
        list(range = c(1, 2), color = "#F17806"),
        list(range = c(2, 3), color = "#FFD700"),
        list(range = c(3, 4), color = "#008B45"))
      )) 
  fig <- fig %>%
    layout(
      margin = list(l=20,r=30, t = 90),
      font = list(color = "#00688B", family = "Arial", size = 25, face="bold"))
  
  fig
})
# renderDataTable()
```

